How to use flowCore package

### 2006-12-01 inst/doc/HowTo-flowCore.Rnw
modify the other transformation functions
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@21330 bc3139a8-67e5-0310-9ffc-ced21a209358

\title{How to use flowCore package}
\author{N. Le Meur F. Hahne P. Haaland}

@@

A linear transformation is like parameter= a*parameter +b
<<linearTransform,echo=FALSE,results=hide>>=
linear <- linearTransform(transformationId="linear-transformation",a=2, b=0)
Bb <- b08
colnames(Bb@exprs) <- paste("c",1:8,sep="")
data08Transform <- transform(Bb,c1=linear(c1))
@ 
\begin{verbatim}
>linear <- linearTransform(transformationId="linear-transformation",a=2, b=0)
>data08Transform <- transform(b08,FCS-H=linear(FCS-H))
\end{verbatim}

@@

A log transformation is of type: parameter=log(parameter,logbase) * r/d
<<logTransform,eval=FALSE,echo=FALSE,results=hide>>=
logTransform <- logTransformation(transformationId="Log-Transformation",
                r=1, d=1,logbase=2)
data08LogTransform <- transform(Bb,c1=logTransform(c1))
@ 
\begin{verbatim}
>logTransform <- logTransformation(transformationId="Log-Transformation", r=1, d=1,logbase=2)
>data08LogTransform <- transform(b08,FCS-H=logTransform(FCS-H))
\end{verbatim}
<<ResultTransfoLinear>>=
b08@exprs[1:5]
#Linear transformation
data08Transform@exprs[1:5]
##Log base 2 transformation
##data08LogTransform@exprs[1:5]
@

>>>>

\title{How to use flowCore package}
\author{N. Le Meur F. Hahne B. Ellis P. Haaland}

@@

A linear transformation is like parameter= a*parameter +b
<<linearTransform,echo=FALSE,results=hide>>=
linear <- linearTransform(transformationId="linear-transformation",a=2, b=0)
data08Transform <- transform(b08,`FSC-H`=linear(`FSC-H`))
@ 
\begin{verbatim}
>linear <- linearTransform(transformationId="linear-transformation",a=2, b=0)
>data08Transform <- transform(b08,`FSC-H`=linear(`FSC-H`))
\end{verbatim}

@@

A log transformation is of type: parameter=log(parameter,logbase) * r/d
<<logTransform,eval=FALSE,echo=FALSE,results=hide>>=
logTransform <- logTransform(transformationId="Log-Transformation",logbase=2,r=1,d=1)
data08LogTransform <- transform(b08,`FSC-H`=logTransform(`FSC-H`))
@ 
\begin{verbatim}
>logTransform <- logTransformation(transformationId="Log-Transformation", r=1, d=1,logbase=2)
>data08LogTransform <- transformb08,`FSC-H`=logTransform(`FSC-H`))
\end{verbatim}

<<ResultTransfoLinear>>=
b08@exprs[1:5]
#Linear transformation
data08Transform@exprs[1:5]
##Log base 2 transformation
##data08LogTransform@exprs[1:5]
@
